---
title: "Eclipse Project Report"
author: "Alambic"
output: pdf_document
---

```{r init, echo=FALSE, message=FALSE}
# Main information
project.id <- 'modeling.gendoc'
plugin.id <- 'EclipseReport'

library(knitr)

knitr::opts_chunk$set(fig.path = paste( 'figures/', plugin.id, '/', project.id, '/', sep=""))
opts_knit$set(progress=TRUE, echo=FALSE, verbose=TRUE, self.contained=T)

require(ggplot2)
library(reshape2)
require(xtable)
require(pander)
require(ggthemes)

# Read files
main <- read.csv(file=paste("", project.id, "_main.csv", sep=""), header=T)
info <- read.csv(file=paste("", project.id, "_info.csv", sep=""), header=T)
metrics <- read.csv(file=paste("", project.id, "_metrics.csv", sep=""), header=T)
attributes <- read.csv(file=paste("", project.id, "_attributes.csv", sep=""), header=T)
recs <- read.csv(file=paste("", project.id, "_recs.csv", sep=""), header=T)


# ITS
file.its.evol <- paste("../../../../projects/", project.id, '/output/', project.id, "_its_evol.csv", sep="")
its.evol <- read.csv(file=file.its.evol, header=T)
its.evol <- its.evol[its.evol$changed != 0,]
project.name <- info[info$Mnemo == 'pmi_title',2]
project.desc <- info[info$Mnemo == 'pmi_desc',2]
run.last <- ''
```

Name: `r project.name` 

Description: `r project.desc`

Last analysis run on `r run.last`.

# Project Information

```{r info, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
panderOptions('table.split.table', Inf)
set.caption( paste( "Information for project ", project.id, sep="" ) )
pandoc.table( main, style = 'multiline', justify = c('left', 'left') )
```

# Metrics

Alambic retrieved `r nrow(metrics)` metrics from xxx data sources: 

```{r metrics, echo=F, message=FALSE, warnings=FALSE, results='asis'}
panderOptions('table.split.table', Inf)
set.caption( paste( "ITS metrics for project ", project.id, sep="" ) )
pandoc.table(metrics, style = 'grid', justify = c('left', 'left'))
```

# Recommendations

`r nrow(metrics)` recommendations have been emitted for this project. 

```{r recs, echo=F, message=FALSE, warnings=FALSE, results='asis'}
#\begin{tabularx}{\linewidth}{ll}
panderOptions('table.split.table', Inf)
set.caption( paste( "Recommendations for project ", project.id, sep="" ) )
pandoc.table(recs, style = 'multiline', justify = c('left', 'left', 'left'))
#\end{tabularx}
```


# Issue Tracking System

Measures have been retrieved from `r its.evol[1,c('date')]` up to `r tail(its.evol, 1)[c('date')]`. Here are a few facts:
\begin{itemize}
\item Month with most open bugs was `r its.evol[which(its.evol$opened == max(its.evol$openers)), c('date')]`.
\end{itemize}


```{r its_ggplot, echo=FALSE, fig.width=10, fig.height=4}
my.data.long <- melt(its.evol[,c("unixtime", "opened", "closed")], id.vars="unixtime", value.name="value", variable.name="metric")
my.data.long$time <- as.POSIXct(as.numeric(as.character(my.data.long$unixtime)), origin="1970-01-01")

p <- ggplot(my.data.long, aes(x = time, y = value, color=metric)) + geom_line(size = .1) + theme_tufte()
p
```


