---
title: "Jira ITS visualisation"
author:
- name: "Boris Baldassari"
  affiliation: Castalia Solutions
output:
  html_fragment:
    toc: false
    fig_caption: true
    fig.width: 800
    self_contained: false
    lib_dir: libs
    echo: false
    dev: svg
---

```{r init, echo=FALSE, message=FALSE}

library(knitr)
library(xts)
library(reshape2)
require(ggplot2)
require(xtable)

knitr::opts_chunk$set(fig.path = 'figures/')

#project.id <- 'modeling.sirius'
plugin.id <- 'JiraIts'
file.evol = paste("", project.id, "_jira_evol.csv", sep="")
file.metrics = paste("", project.id, "_jira.csv", sep="")

evol <- read.csv(file=file.evol, header=T)
metrics <- read.csv(file=file.metrics, header=T)
```

## Jira Issue Tracking System

<br />

<div class="row"><div class="col-sm-7">

The JIRA repository for the project contains ``r metrics[['JIRA_VOL']]`` issues created by ``r metrics[['JIRA_AUTHORS']]`` authors. The first issue was created the ``r evol[1,1]`` and the last analysed issue was created on ``r evol[nrow(evol),1]``.

During the last month, there has been ``r metrics[['JIRA_CREATED_1M']]`` issues created by ``r metrics[['JIRA_AUTHORS_1M']]`` authors.

</div><div class="col-sm-4">
  <div class="panel panel-default">
  <div class="panel-heading"><h3 class="panel-title">Contents</h3></div>
  <div class="list-group">
  <a href="#summary" class="list-group-item">Quick Summary</a>
  <a href="#authors" class="list-group-item">Authors</a>
  <a href="#commits" class="list-group-item">Issues created</a>
  <a href="#downloads" class="list-group-item">Downloads</a>
  </div>
  </div>
</div></div>

### <a name="quick-summary"></a>Quick Summary

``r ncol(metrics)`` static metrics relative to the current project state have been retrieved:

```{r metrics_table, echo=FALSE, message=FALSE, results='asis'}
t <- lapply(names(metrics), function(x) paste(x, ' <span class="badge">', metrics[[x]], '</span>, ', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```

The evolution of ``r ncol(evol)`` metrics has been retrieved: ``r paste(names(evol), collapse=", ")``.

The following plot uses the [plotly library](http://plot.ly) to enable users to play with data itself, and its associated plot. Hover on the graph for more options.

<iframe src="/projects/`r project.id`/JiraIts/jira_evol_summary.html" frameborder="0" style="width: 100%; height: 360px"></iframe>

-----

### <a name="people"></a>Authors

The following plot shows the evolution of [authors](/documentation/metrics#SCM_AUTHORS) during the overall time range covered by the analysis.

<iframe src="/projects/`r project.id`/JiraIts/jira_evol_authors.html" frameborder="0" style="width: 100%; height: 300px"></iframe>

-----

### <a name="commits"></a>Created

The following plot shows the evolution of [commits](/documentation/metrics#SCM_COMMITS) during the overall time range covered by the analysis.

<iframe src="/projects/`r project.id`/JiraIts/jira_evol_created.html" frameborder="0" style="width: 100%; height: 300px"></iframe>

-----

### <a name="downloads"></a>Downloads

The visualisations on this page can be exported and easily reused on an external web site. You can find more information on iframes and pictures reuse in [the project&apos;s wiki](https://bitbucket.org/BorisBaldassari/alambic/wiki/Using_autogenerated_pictures/). Remember to change the server name in the code samples provided.

Plot of main evolution metrics of the configuration management system

    <iframe src="http://server/projects/`r project.id`/JiraIts/jira_evol_summary.html" frameborder="0" style="width: 100%; height: 720px"></iframe>

Evolution of authors and committers

    <iframe src="http://server/projects/`r project.id`/JiraIts/jira_evol_authors.html" frameborder="0" style="width: 100%; height: 300px"></iframe>

Evolution of commits

    <iframe src="http://server/projects/`r project.id`/JiraIts/jira_evol_commits.html" frameborder="0" style="width: 100%; height: 300px"></iframe>

The visualisations used in this document rely on a number of flat CSV and JSON data files. You can download and play with them if you want to thereafter:

* The original file of current information, downloaded from the Jira server [ <a href="import_jira.json">Download JSON</a> ]
* The evolution of issues created and authors by day [ <a href="jira_evol.csv">Download CSV</a> ]
* The list of issues, with fields 'id, summary, status, assignee, reporter, due_date, created_at, updated_at'  [ <a href="jira_issues.csv">Download CSV</a> ]
* The list of late issues (i.e. their due_date has past), with fields 'id, summary, status, assignee, reporter, due_date, created_at, updated_at' [ <a href="jira_issues_late.csv">Download CSV</a> ]
* The list of open issues, with fields 'id, summary, status, assignee, reporter, due_date, created_at, updated_at' [ <a href="jira_issues_open.csv">Download CSV</a> ]
* The list of open and unassigned issues, with fields 'id, summary, status, assignee, reporter, due_date, created_at, updated_at' [ <a href="jira_issues_open_unassigned.csv">Download CSV</a> ]




