---
#########################################################
#
# Copyright (c) 2015-2017 Castalia Solutions and others.
#
# All rights reserved. This program and the accompanying materials
# are made available under the terms of the Eclipse Public License v1.0
# which accompanies this distribution, and is available at
# http://www.eclipse.org/legal/epl-v10.html
#
# Contributors:
#   Boris Baldassari - Castalia Solutions
#
#########################################################

title: "GitLab Project visualisation"
author:
- name: "Boris Baldassari"
  affiliation: Castalia Solutions
output:
  html_fragment:
    toc: false
    fig_caption: true
    fig.width: 800
    self_contained: false
    lib_dir: libs
    echo: false
    dev: svg
---

```{r init, echo=FALSE, message=FALSE}
library(knitr)
library(xts)
library(reshape2)
require(ggplot2)
require(xtable)

knitr::opts_chunk$set(fig.path = "figures/")

suppressPackageStartupMessages(library(googleVis))
options(gvis.plot.tag='chart')
require('reshape2')

# Enable font awesome
htmltools::tagList(rmarkdown::html_dependency_font_awesome())

# Plugin needs the following parameters:
#   * project.id
#   * gitlab.id
#   * gitlab.url

project.id <- 'alambic'
gitlab.id <- 'bbaldassari/Alambic'
gitlab.url <- 'https://gitlab.com'
plugin.id <- 'GitLabProject'
file.metrics = paste("../../../../projects/", project.id, "/output/", project.id, "_metrics_gitlab_project.csv", sep="")
file.info = paste("../../../../projects/", project.id, "/output/", project.id, "_info_gitlab_project.csv", sep="")
file.commits.hist = paste("../../../../projects/", project.id, "/output/", project.id, "_gitlab_git_commits_hist.csv", sep="")
file.commits = paste("../../../../projects/", project.id, "/output/", project.id, "_gitlab_git_commits.csv", sep="")
file.branches = paste("../../../../projects/", project.id, "/output/", project.id, "_gitlab_project_branches.csv", sep="")
file.mrs = paste("../../../../projects/", project.id, "/output/", project.id, "_gitlab_git_merge_requests.csv", sep="")
file.milestones = paste("../../../../projects/", project.id, "/output/", project.id, "_gitlab_project_milestones.csv", sep="")

metrics <- read.csv(file=file.metrics, header=T)
info <- read.csv(file=file.info, header=T)
commits <- read.csv(file=file.commits, header=T)
commits.hist <- read.csv(file=file.commits.hist, header=T)
branches <- read.csv(file=file.branches, header=T)
mrs <- read.csv(file=file.mrs, header=T)
milestones <- read.csv(file=file.milestones, header=T)

geticon <- function(value) {
  if (value == 1) {
    return('fa-check-square-o') 
  } else {
    return('fa-square-o') 
  }
}

# Configuration of visuals
list.mrs.count <- 5
```

## GitLab Project `r gitlab.id`

<br />

<div class="row"><div class="col-sm-7">

GitLab offers generic hosting services for software development. This plugin retrieves information about the project and its statistics, and computes metrics and recommendations. GitLab offers a [complete API](https://docs.gitlab.com/ee/api/README.html) to interact with a GitLab server, and Perl has a ready-to-use [module that cover the API&apos;s features](http://search.cpan.org/~bluefeet/GitLab-API-v3-0.08/lib/GitLab/API/v3.pm).

Data for project is directly available from the project&apos;s dashboard:

* Project summary: `r gitlab.url`/`r gitlab.id`
* Commits: `r info['PROJECT_COMMITS_URL']` 
* Merge Requests: `r info['PROJECT_MRS_URL']` <i class="fa `r geticon(info['PROJECT_MRS_ENABLED'])`"></i>
* CI: `r info['PROJECT_CI_URL']` <i class="fa `r geticon(info['PROJECT_CI_ENABLED'])`"></i>
* Issues: `r info['PROJECT_ISSUES_URL']` <i class="fa `r geticon(info['PROJECT_ISSUES_ENABLED'])`"></i>
* Wiki: `r info['PROJECT_WIKI_URL']` <i class="fa `r geticon(info['PROJECT_WIKI_ENABLED'])`"></i>

</div><div class="col-sm-4">
  <div class="panel panel-default">
  <div class="panel-heading"><h3 class="panel-title">Contents</h3></div>
  <div class="list-group">
  <a href="#summary" class="list-group-item">Quick Summary</a>
  <a href="#commits" class="list-group-item">Commits</a>
  <a href="#branches" class="list-group-item">Branches</a>
  <a href="#mrs" class="list-group-item">Merge Requests</a>
  <a href="#mrs" class="list-group-item">Milestones</a>
  </div>
  </div>
</div></div>

### <a name="quick-summary"></a>Quick Summary

The project was created on `r info[['PROJECT_CREATED_AT']]` and was last updated on `r metrics[['PROJECT_LAST_ACTIVITY_AT']]`.

The URLs to use to connect to the repository are:

* SSH ``r info[['PROJECT_REPO_SSH']]``.
* HTTP ``r info[['PROJECT_REPO_HTTP']]``.

There is a total of `r ncol(metrics)` metrics retrieved:

```{r metrics_table, echo=FALSE, message=FALSE, results='asis'}
t <- lapply(names(metrics), function(x) paste(x, ' <span class="badge">', metrics[[x]], '</span>, ', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```

There is a total of `r ncol(info)` information retrieved:

```{r info_table, echo=FALSE, message=FALSE, results='asis'}
t <- lapply(names(info), function(x) paste(x, ' <span class="badge">', info[[x]], '</span>, ', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```

-----

### <a name="commits"></a> Commits

There has been a total of `r metrics[['PROJECT_COMMITS']]` commits on the git repository (`r metrics[['PROJECT_COMMITS_1W']]` during last week, `r metrics[['PROJECT_COMMITS_1M']]` during last month, `r metrics[['PROJECT_COMMITS_1Y']]` during last year).

`r metrics[['PROJECT_AUTHORS']]` authors have contributed during the lifetime of the project (`r metrics[['PROJECT_AUTHORS']]` during last week, `r metrics[['PROJECT_AUTHORS']]` during last month, and `r metrics[['PROJECT_AUTHORS']]` during last year).

-----

### <a name="branches"></a> Branches

The following branches are defined in the Git repository, sorted by last activity date.

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Git Branches</div>

<table class="table table-striped">
  <tr><th>Name</th><th>Commit title</th><th>Last commit date</th><th>Last committer</th></tr>
```{r branches_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(branches[order(branches$commit_date, decreasing = T),], 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[3]], '</td><td>',
							    x[[4]], '</td><td>', x[[6]], '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

-----

### <a name="mrs"></a> Merge Requests

Summary:

* Total number of merge requests: `r metrics[['PROJECT_MRS_OPENED']]`.
* Number of merge requests opened during last week: `r metrics[['PROJECT_MRS_OPENED_1W']]`, last month: `r metrics[['PROJECT_MRS_OPENED_1M']]`, last year: `r metrics[['PROJECT_MRS_OPENED_1Y']]`

Activity: 

* `r metrics[['PROJECT_MRS_OPENED_STALLED_1M']]` merge requests are open and have had no update since more than one month.
* `r metrics[['PROJECT_MRS_OPENED_STILL_1W']]` merge requests have been opened for more than one week, `r metrics[['PROJECT_MRS_OPENED_STILL_1M']]` for more than 1 month, and `r metrics[['PROJECT_MRS_OPENED_STILL_1Y']]` for more than one year.
* `r metrics[['PROJECT_MRS_OPENED_STILL_1M']]` merge requests are open and have had no update since more than one month.

The following open merge requests are currently available:

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span>  Open Merge Requests</div>

<table class="table table-striped">
  <tr><th>ID</th><th>State</th><th>Title</th><th>Assignee</th><th>Source branch</th><th>Target branch</th><th>Created</th><th>Updated</th></tr>
```{r mrs_table_open, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(mrs[mrs$state == 'opened',], 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[3]], '</td><td><a href="',
		           x[[6]], '">', x[[2]], '</a></td><td>', x[[5]], '</td><td>', x[[10]],
							 '</td><td>', x[[12]],'</td><td>', x[[14]], '</td><td>', x[[15]], 
							 '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

The following merged merge requests are currently available. Only the last `r list.mrs.count` merge requests are listed.

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span>  Open Merge Requests</div>

<table class="table table-striped">
  <tr><th>ID</th><th>State</th><th>Title</th><th>Assignee</th><th>Source branch</th><th>Target branch</th><th>Created</th><th>Updated</th></tr>
```{r mrs_table_merged, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(head(mrs[mrs$state == 'merged',], n=list.mrs.count), 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[3]], '</td><td><a href="',
		           x[[6]], '">', x[[2]], '</a></td><td>', x[[5]], '</td><td>', x[[10]],
							 '</td><td>', x[[12]],'</td><td>', x[[14]], '</td><td>', x[[15]], 
							 '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

-----

### <a name="milestones"></a> Milestones

The following plots show the number of issues (opened, closed) on all active milestones for the project.

<div class="row">
```{r milestones_donuts, echo=FALSE, message=FALSE, results='asis'}
for (i in 1:nrow(milestones[milestones$state == 'active',])) {
  cat('<div class="col-md-3">')
  ms <- data.frame(unlist(c('issues_opened', 'issues_closed')), unlist(milestones[i,c('issues_opened', 'issues_closed')]))

  p <- gvisPieChart(ms,
                  options = list(
                    title=paste("Issues for milestone ", milestones[i,3], sep=""),
                    colors="['red', 'green']",
                    width=350, height=280,
                    pieHole= 0.4))

  print(p, 'chart')
  cat('</div>')
}
```
</div>


<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Active Milestones</div>

<table class="table table-striped">
  <tr><th>ID</th><th>IID</th><th>Title</th><th>Description</th><th>Issues (open/total)</th><th>Start date</th><th>Due date</th><th>Created</th><th>Updated</th></tr>
```{r milestones_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(milestones[milestones$state == 'active',], 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[2]], '</td><td>',
		           x[[3]], '</td><td>', x[[4]], '</td><td>', x[[11]], ' / ', x[[10]],
							 '</td><td>', x[[7]],'</td><td>', x[[6]], '</td><td>', x[[8]], 
							 '</td><td>', x[[9]], '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>
