---
#########################################################
#
# Copyright (c) 2015-2017 Castalia Solutions and others.
#
# All rights reserved. This program and the accompanying materials
# are made available under the terms of the Eclipse Public License v1.0
# which accompanies this distribution, and is available at
# http://www.eclipse.org/legal/epl-v10.html
#
# Contributors:
#   Boris Baldassari - Castalia Solutions
#
#########################################################

title: "GitLab Project visualisation"
author:
- name: "Boris Baldassari"
  affiliation: Castalia Solutions
output:
  html_fragment:
    toc: false
    fig_caption: true
    fig.width: 800
    self_contained: false
    lib_dir: libs
    echo: false
    dev: svg
---

```{r init, echo=FALSE, message=FALSE}
library(knitr)
library(xts)
require('reshape2')
require(ggplot2)
require(xtable)

knitr::opts_chunk$set(fig.path = "figures/")

suppressPackageStartupMessages(library(googleVis))
options(gvis.plot.tag='chart')

# Enable font awesome
htmltools::tagList(rmarkdown::html_dependency_font_awesome())

# Plugin needs the following parameters:
#   * project.id
#   * gitlab.id
#   * gitlab.url

# project.id <- 'inkscape'
# gitlab.id <- 'inkscape/inkscape'
# gitlab.url <- 'https://gitlab.com'

# project.id <- 'gitlab-runner'
# gitlab.id <- 'gitlab-org/gitlab-runner'
# gitlab.url <- 'https://gitlab.com'

#project.id <- 'alambic'
#gitlab.id <- 'bbaldassari/Alambic'
#gitlab.url <- 'https://gitlab.com'
plugin.id <- 'GitLabProject'
file.metrics = paste("../../../../projects/", project.id, "/output/", project.id, "_metrics_gitlab_project.csv", sep="")
file.info = paste("../../../../projects/", project.id, "/output/", project.id, "_info_gitlab_project.csv", sep="")
file.commits.hist = paste("../../../../projects/", project.id, "/output/", project.id, "_gitlab_git_commits_hist.csv", sep="")
file.commits = paste("../../../../projects/", project.id, "/output/", project.id, "_gitlab_git_commits.csv", sep="")
file.branches = paste("../../../../projects/", project.id, "/output/", project.id, "_gitlab_project_branches.csv", sep="")
file.mrs = paste("../../../../projects/", project.id, "/output/", project.id, "_gitlab_git_merge_requests.csv", sep="")
file.milestones = paste("../../../../projects/", project.id, "/output/", project.id, "_gitlab_project_milestones.csv", sep="")

metrics <- read.csv(file=file.metrics, header=T)
info <- read.csv(file=file.info, header=T)
commits <- read.csv(file=file.commits, header=T)
commits.hist <- read.csv(file=file.commits.hist, header=T)
branches <- read.csv(file=file.branches, header=T)
mrs <- read.csv(file=file.mrs, header=T)
milestones <- read.csv(file=file.milestones, header=T)
milestones.active <- milestones[milestones$state == 'active',]

geticon <- function(value) {
  if (is.na(value)) { value <- FALSE }
  if (value == 1) {
    return('fa-check-square-o') 
  } else {
    return('fa-square-o') 
  }
}

# Configuration of visuals
list.mrs.count.opened <- 10
list.mrs.count.merged <- 5
```

## GitLab Project `r gitlab.id`

<br />

<div class="row"><div class="col-sm-7">

GitLab offers generic hosting services for software development. This plugin retrieves information about the project and its statistics, and computes metrics and recommendations. GitLab offers a [complete API](https://docs.gitlab.com/ee/api/README.html) to interact with a GitLab server, and Perl has a ready-to-use [module that cover the API&apos;s features](http://search.cpan.org/~bluefeet/GitLab-API-v3-0.08/lib/GitLab/API/v3.pm).

Data for project is directly available from the project&apos;s dashboard:

* Project Summary: `r gitlab.url`/`r gitlab.id`
* Commits: `r info['PROJECT_COMMITS_URL']` 
* Merge Requests: <i class="fa `r geticon(info['PROJECT_MRS_ENABLED'])`"></i> `r info['PROJECT_MRS_URL']`
* CI: <i class="fa `r geticon(info['PROJECT_CI_ENABLED'])`"></i> `r info['PROJECT_CI_URL']`
* Issues: <i class="fa `r geticon(info['PROJECT_ISSUES_ENABLED'])`"></i> `r info['PROJECT_ISSUES_URL']`
* Wiki: <i class="fa `r geticon(info['PROJECT_WIKI_ENABLED'])`"></i> `r info['PROJECT_WIKI_URL']`

The URLs to use to connect to the repository are:

* SSH ``r info[['PROJECT_REPO_SSH']]``.
* HTTP ``r info[['PROJECT_REPO_HTTP']]``.

</div><div class="col-sm-4">
  <div class="panel panel-default">
  <div class="panel-heading"><h3 class="panel-title">Contents</h3></div>
  <div class="list-group">
  <a href="#summary" class="list-group-item">Quick Summary</a>
  <a href="#mrs" class="list-group-item">Milestones</a>
  <a href="#commits" class="list-group-item">Commits</a>
  <a href="#branches" class="list-group-item">Branches</a>
  <a href="#mrs" class="list-group-item">Merge Requests</a>
  </div>
  </div>
</div></div>

### <a name="quick-summary"></a>Quick Summary

The project was created on ``r info[['PROJECT_CREATED_AT']]`` and was last updated on ``r metrics[['PROJECT_LAST_ACTIVITY_AT']]``.

<div class="row"><div class="col-sm-3">
<span style="font-size:18pt"><span class="fa fa-heartbeat"></span> </span>
</div><div class="col-sm-3">
<span><span style="font-size:24pt">``r trimws(metrics[['PROJECT_FORKS']], which='both')``</span> Forks</span>
</div><div class="col-sm-3">
<span><span style="font-size:24pt">``r trimws(metrics[['PROJECT_STARS']], which='both')``</span> Stars</span>
</div><div class="col-sm-3">
<span><span style="font-size:24pt">``r trimws(metrics[['PROJECT_ISSUES_OPEN']], which='both')``</span> Issues open</span>
</div></div>

Git activity during last month:

<div class="row"><div class="col-sm-3">
<span style="font-size:18pt"><span class="fa fa-git"></span> </span>
</div><div class="col-sm-3">
<span><span style="font-size:24pt">``r trimws(metrics[['PROJECT_COMMITS_1M']], which='both')``</span> Commits</span>
</div><div class="col-sm-3">
<span><span style="font-size:24pt">``r trimws(metrics[['PROJECT_COMMITTERS_1M']], which='both')``</span> Committers</span>
</div><div class="col-sm-3">
<span><span style="font-size:24pt">``r trimws(metrics[['PROJECT_AUTHORS_1M']], which='both')``</span> Authors</span>
</div></div>

Merge Requests activity during last month:

<div class="row"><div class="col-sm-3">
<span style="font-size:18pt"><span class="fa fa-random"></span> </span>
</div><div class="col-sm-3">
<span><span style="font-size:24pt">``r trimws(metrics[['SCM_PRS_OPENED_1M']], which='both')``</span> MRs created last month</span>
</div><div class="col-sm-3">
<span><span style="font-size:24pt">``r trimws(metrics[['SCM_PRS_OPENED_STILL_1M']], which='both')``</span> MRs created within last month and still opened</span>
</div><div class="col-sm-3">
<span><span style="font-size:24pt">``r trimws(metrics[['SCM_PRS_OPENED_STALED_1M']], which='both')``</span> MRs staled (no update) for one month</span>
</div></div>

There is a total of ``r ncol(metrics)`` metrics retrieved.

```{r metrics_table, echo=FALSE, message=FALSE, results='asis'}
t <- lapply(names(metrics), function(x) paste(x, ' <span class="badge">', metrics[[x]], '</span>, ', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```

There is a total of ``r ncol(info)`` information retrieved:

```{r info_table, echo=FALSE, message=FALSE, results='asis'}
t <- lapply(names(info), function(x) paste('* ', x, ': ', info[[x]], "\n", sep=''))
t <- paste(t, collapse="")
cat(t)
```

-----

### <a name="milestones"></a> Milestones

The following plot show the number of issues (opened, closed) on all active milestones for the project.

<div class="row">
```{r milestones_donuts, eval=nrow(milestones.active)>0, echo=FALSE, message=FALSE, results='asis'}
for (i in 1:nrow(milestones.active)) {
  cat('<div class="col-md-3">')
  ms <- data.frame(unlist(c('issues_opened', 'issues_closed')), unlist(milestones.active[i,c('issues_opened', 'issues_closed')]))
  
  p <- gvisPieChart(ms,
                  options = list(
                    title=paste("Issues for milestone ", milestones.active[i,4], sep=""),
                    colors="['red', 'green']",
                    width=350, height=280,
                    pieHole= 0.4))
  print(p, 'chart')
  cat('</div>')
}
```
</div>


<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Active Milestones</div>

<table class="table table-striped">
  <tr><th>IID</th><th>ID</th><th>Title</th><th>Issues (open/total)</th><th>Start date</th><th>Due date</th><th>Created</th><th>Updated</th></tr>
```{r milestones_table, eval=nrow(milestones.active)>0, echo=FALSE, message=FALSE, results='asis'}
t <- apply(milestones.active, 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[2]], '</td><td>',
		           x[[4]], '</td><td>', x[[11]], ' / ', x[[10]],
							 '</td><td>', x[[7]],'</td><td>', x[[8]], '</td><td>', as.Date(x[[5]]), 
							 '</td><td>', as.Date(x[[6]]), '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

-----

### <a name="commits"></a> Commits

There has been a total of ``r metrics[['PROJECT_COMMITS']]`` commits on the git repository (``r metrics[['PROJECT_COMMITS_1W']]`` during last week, ``r metrics[['PROJECT_COMMITS_1M']]`` during last month, ``r metrics[['PROJECT_COMMITS_1Y']]`` during last year).

``r metrics[['PROJECT_AUTHORS']]`` authors have contributed during the lifetime of the project (``r metrics[['PROJECT_AUTHORS_1W']]`` during last week, ``r metrics[['PROJECT_AUTHORS_1M']]`` during last month, and ``r metrics[['PROJECT_AUTHORS_1Y']]`` during last year).

-----

### <a name="branches"></a> Branches

The following branches are defined in the Git repository, sorted by last activity date.

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Git Branches</div>

<table class="table table-striped">
  <tr><th>Name</th><th>Commit title</th><th>Last commit date</th><th>Last committer</th></tr>
```{r branches_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(branches[order(branches$commit_date, decreasing = T),], 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[3]], '</td><td>',
							    x[[4]], '</td><td>', x[[6]], '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

-----

### <a name="mrs"></a> Merge Requests

Summary:

* Total number of merge requests: ``r metrics[['SCM_PRS']]``, total number of open merge requests: ``r metrics[['SCM_PRS_OPENED']]``.
* Number of merge requests opened during last week: ``r metrics[['SCM_PRS_OPENED_1W']]``, last month: ``r metrics[['SCM_PRS_OPENED_1M']]``, last year: ``r metrics[['SCM_PRS_OPENED_1Y']]``.

Activity: 

* ``r metrics[['SCM_PRS_OPENED_STALED_1M']]`` merge requests are open and have had no update since more than one month.
* ``r metrics[['SCM_PRS_OPENED_STILL_1W']]`` merge requests have been opened for more than one week, ``r metrics[['SCM_PRS_OPENED_STILL_1M']]`` for more than 1 month, and ``r metrics[['SCM_PRS_OPENED_STILL_1Y']]`` for more than one year.

The following open merge requests are currently available. Only the last `r list.mrs.count.opened` merge requests are listed.

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span>  Open Merge Requests</div>

<table class="table table-striped">
  <tr><th>ID</th><th>State</th><th>Title</th><th>Assignee</th><th>Source branch</th><th>Target branch</th><th>Created</th><th>Updated</th></tr>
```{r mrs_table_open, eval=T, echo=FALSE, message=FALSE, results='asis'}
mrs_opened <- mrs[mrs$state == 'opened',]
t <- apply(head(mrs_opened, n = list.mrs.count.opened), 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[3]], '</td><td><a href="',
		           x[[6]], '">', x[[2]], '</a></td><td>', x[[5]], '</td><td>', x[[10]],
							 '</td><td>', x[[12]],'</td><td>', as.POSIXct(as.integer(x[[18]]), origin="1970-01-01"), 
							 '</td><td>', as.POSIXct(as.integer(x[[19]]), origin="1970-01-01"), 
							 '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

The following merged merge requests are currently available. Only the last `r list.mrs.count.merged` merge requests are listed.

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span>  Merged Merge Requests</div>

<table class="table table-striped">
  <tr><th>ID</th><th>State</th><th>Title</th><th>Assignee</th><th>Source branch</th><th>Target branch</th><th>Created</th><th>Updated</th></tr>
```{r mrs_table_merged, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(head(mrs[mrs$state == 'merged',], n=list.mrs.count.merged), 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[3]], '</td><td><a href="',
		           x[[6]], '">', x[[2]], '</a></td><td>', x[[5]], '</td><td>', x[[10]],
							 '</td><td>', x[[12]],'</td><td>', as.POSIXct(as.integer(x[[18]]), origin="1970-01-01"), 
							 '</td><td>', as.POSIXct(as.integer(x[[19]]), origin="1970-01-01"), 
							 '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

