---
#########################################################
#
# Copyright (c) 2015-2020 Castalia Solutions and others.
#
# All rights reserved. This program and the accompanying materials
# are made available under the terms of the Eclipse Public License v1.0
# which accompanies this distribution, and is available at
# http://www.eclipse.org/legal/epl-v10.html
#
# Contributors:
#   Boris Baldassari - Castalia Solutions
#
#########################################################

title: "GitHub Project visualisation"
author:
- name: "Boris Baldassari"
  affiliation: Castalia Solutions
output:
  html_fragment:
    toc: false
    fig_caption: true
    fig.width: 800
    self_contained: false
    lib_dir: libs
    echo: false
    dev: svg
---

```{r init, echo=FALSE, message=FALSE}
library(knitr)
library(xts)
require('reshape2')
require(ggplot2)
require(xtable)

knitr::opts_chunk$set(fig.path = "figures/")

suppressPackageStartupMessages(library(googleVis))
options(gvis.plot.tag='chart')

# Enable font awesome
htmltools::tagList(rmarkdown::html_dependency_font_awesome())

# Plugin needs the following parameters:
#   * project.id
#   * github.user
#   * github.repo
#   * github.url

# project.id <- 'test.github.project'
# github.url <- 'https://api.github.com'
# github.user <- 'crossminer'
# github.repo <- 'crossflow'

plugin.id <- 'GitHubProject'
file.metrics = paste("../../../../projects/", project.id, "/output/", project.id, "_metrics_github_project.csv", sep="")
file.info = paste("../../../../projects/", project.id, "/output/", project.id, "_info_github_project.csv", sep="")
file.contribs = paste("../../../../projects/", project.id, "/output/", project.id, "_github_project_contributors.csv", sep="")
file.langs = paste("../../../../projects/", project.id, "/output/", project.id, "_github_project_languages.csv", sep="")
file.events = paste("../../../../projects/", project.id, "/output/", project.id, "_github_project_events.csv", sep="")

metrics <- read.csv(file=file.metrics, header=T)
info <- read.csv(file=file.info, header=T)
contribs <- read.csv(file=file.contribs, header=T)
langs <- read.csv(file=file.langs, header=T)
events <- read.csv(file=file.events, header=T)

geticon <- function(value) {
  if (is.na(value)) { value <- FALSE }
  if (value == 1) {
    return('fa-check-square-o') 
  } else {
    return('fa-square-o') 
  }
}

```

## GitHub Project `r github.user`/`r github.repo` 

<br />

<div class="row"><div class="col-sm-7">

github offers generic hosting services for software development. This plugin retrieves information about the project and its statistics, and computes metrics and recommendations. github offers a [complete API](https://docs.github.com/ee/api/README.html) to interact with a github server, and Perl has a ready-to-use [module that cover the API&apos;s features](http://search.cpan.org/~bluefeet/github-API-v3-0.08/lib/github/API/v3.pm).

Data for project is directly available from the project&apos;s dashboard:

* Project ID: `r github.user`/`r github.repo`
* Project URL: `r info['PROJECT_URL']` 
* Commits: `r info['PROJECT_COMMITS_URL']` 
* DL: <i class="fa `r geticon(info['PROJECT_DL_ENABLED'])`"></i> `r info['PROJECT_DL_URL']`
* Issues: <i class="fa `r geticon(info['PROJECT_ISSUES_ENABLED'])`"></i> `r info['PROJECT_ISSUES_URL']`
* Wiki: <i class="fa `r geticon(info['PROJECT_WIKI_ENABLED'])`"></i> `r info['PROJECT_WIKI_URL']`

The URLs to use to connect to the repository are:

* SSH ``r info[['PROJECT_REPO_SSH']]``.
* GIT ``r info[['PROJECT_REPO_GIT']]``.
* HTTP ``r info[['PROJECT_REPO_HTTP']]``.

</div><div class="col-sm-4">
  <div class="panel panel-default">
  <div class="panel-heading"><h3 class="panel-title">Contents</h3></div>
  <div class="list-group">
  <a href="#summary" class="list-group-item">Quick Summary</a>
  <a href="#mrs" class="list-group-item">Milestones</a>
  <a href="#commits" class="list-group-item">Commits</a>
  <a href="#branches" class="list-group-item">Branches</a>
  <a href="#mrs" class="list-group-item">Merge Requests</a>
  </div>
  </div>
</div></div>

### <a name="quick-summary"></a>Quick Summary

The project was created on ``r info[['PROJECT_CREATED_AT']]`` and was last updated on ``r info[['PROJECT_LAST_ACTIVITY_AT']]``.

<div class="row"><div class="col-sm-3">
<span><span style="font-size:24pt">``r trimws(metrics[['PROJECT_FORKS']], which='both')``</span> Forks</span>
</div><div class="col-sm-3">
<span><span style="font-size:24pt">``r trimws(metrics[['PROJECT_STARS']], which='both')``</span> Stars</span>
</div><div class="col-sm-3">
<span><span style="font-size:24pt">``r trimws(metrics[['PROJECT_STARGAZERS']], which='both')``</span> Stargazers</span>
</div><div class="col-sm-3">
<span><span style="font-size:24pt">``r trimws(metrics[['PROJECT_WATCHERS']], which='both')``</span> Watchers</span>
</div></div>

There is a total of ``r ncol(metrics)`` metrics retrieved.

```{r metrics_table, echo=FALSE, message=FALSE, results='asis'}
t <- lapply(names(metrics), function(x) paste(x, ' <span class="badge">', metrics[[x]], '</span>, ', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```

There is a total of ``r ncol(info)`` information retrieved:

```{r info_table, echo=FALSE, message=FALSE, results='asis'}
t <- lapply(names(info), function(x) paste('* ', x, ': ', info[[x]], "\n", sep=''))
t <- paste(t, collapse="")
cat(t)
```

-----

<div class="row">
<div class="col-md-6">

### <a name="langs"></a> Languages

The following languages have been found in the Git repository, sorted by lines count:

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Languages</div>

<table class="table table-striped">
  <tr><th>Languages</th><th>Lines Count</th></tr>
```{r langs_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(langs[order(langs$count, decreasing = T),], 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[2]], '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

</div>
<div class="col-md-6">
  <iframe src="/projects/`r project.id`/GitHubProject/github_project_languages_pie.html" frameborder="0" style="width: 500px; height: 340px"></iframe>
</div>
</div>

-----

<div class="row">
<div class="col-md-6">

### <a name="contribs"></a> Contributors

The following contributors have been found in the Git repository, sorted by lines count:

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Contributors</div>

<table class="table table-striped">
  <tr><th>ID</th><th>Login</th><th>Contributions</th><th>URL</th></tr>
```{r contribs_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(contribs[order(contribs$contributions, decreasing = T),], 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[2]], '</td><td>',
							    x[[3]], '</td><td><a href="', x[[4]], '">', x[[4]], '</a></td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

</div>
<div class="col-md-6">
  <iframe src="/projects/`r project.id`/GitHubProject/github_project_contributors_pie.html" frameborder="0" style="width: 500px; height: 340px"></iframe>
</div>
</div>

-----

### <a name="events"></a> Events

The following contributors have been found in the Git repository, sorted by lines count:

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Repository Languages</div>

<table class="table table-striped">
  <tr><th>Type</th><th>Actor ID</th><th>Actor Name</th><th>Created at</th></tr>
```{r events_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(events, 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[2]], '</td><td>',
							    x[[3]], '</td><td>', x[[4]], '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

