---
title: "GitLab ITS visualisation"
author:
- name: "Boris Baldassari"
  affiliation: Castalia Solutions
output:
  html_fragment:
    toc: false
    fig_caption: true
    fig.width: 800
    self_contained: false
    lib_dir: libs
    echo: false
    dev: svg
---

```{r init, echo=FALSE, message=FALSE}
library(knitr)
library(xts)
library(reshape2)
require(ggplot2)
require(xtable)

suppressPackageStartupMessages(library(googleVis))
options(gvis.plot.tag='chart')

knitr::opts_chunk$set(fig.path = "figures/")

# Plugin needs the following parameters:
#   * project.id
#   * gitlab.id
#   * gitlab.url

#project.id <- 'alambic'
#gitlab.id <- 'bbaldassari/Alambic'
#gitlab.url <- 'https://gitlab.com'
plugin.id <- 'GitLabIts'
file.metrics = paste("../../../../projects/", project.id, "/output/", project.id, "_metrics_gitlab_its.csv", sep="")
#file.info = paste("../../../../projects/", project.id, "/output/", project.id, "_info_gitlab_its.csv", sep="")
file.milestones = paste("../../../../projects/", project.id, "/output/", project.id, "_gitlab_its_milestones.csv", sep="")
file.issues = paste("../../../../projects/", project.id, "/output/", project.id, "_gitlab_its_issues.csv", sep="")
file.issues.late = paste("../../../../projects/", project.id, "/output/", project.id, "_gitlab_its_issues_late.csv", sep="")
file.issues.open = paste("../../../../projects/", project.id, "/output/", project.id, "_gitlab_its_issues_open.csv", sep="")
file.issues.unassigned.open = paste("../../../../projects/", project.id, "/output/", project.id, "_gitlab_its_issues_unassigned_open.csv", sep="")

metrics <- read.csv(file=file.metrics, header=T)
#info <- read.csv(file=file.info, header=T)
milestones <- read.csv(file=file.milestones, header=T)
issues <- read.csv(file=file.issues, header=T)
issues.late <- read.csv(file=file.issues.late, header=T)
issues.open <- read.csv(file=file.issues.open, header=T)
issues.unassigned.open <- read.csv(file=file.issues.unassigned.open, header=T)
evol <- xts(x = issues, order.by = as.POSIXct(issues$created_at))
evol.weekly <- apply.weekly(x=evol, FUN = nrow)

```

## GitLab ITS

<br />

<div class="row"><div class="col-sm-7">

GitLab provides a complete set of features for the development of software product, including an [Issue Tracking  System](https://docs.gitlab.com/ee/user/project/issues/). This plugin retrieves information about issues and milestones for the specified project, and computes metrics and recommendations. GitLab offers a [complete API](https://docs.gitlab.com/ee/api/README.html) to interact with a GitLab server, and Perl has a ready-to-use [module that cover the API&apos;s features](http://search.cpan.org/~bluefeet/GitLab-API-v3-0.08/lib/GitLab/API/v3.pm).

Data for project is directly available from the project&apos;s dashboard:

* project Summary: `r gitlab.url`/`r gitlab.id`
* Issues: `r gitlab.url`/`r gitlab.id`/issues
* Milestones: `r gitlab.url`/`r gitlab.id`/milestones

</div><div class="col-sm-4">
  <div class="panel panel-default">
  <div class="panel-heading"><h3 class="panel-title">Contents</h3></div>
  <div class="list-group">
  <a href="#summary" class="list-group-item">Quick Summary</a>
  <a href="#milestones" class="list-group-item">Milestones</a>
  <a href="#late_issues" class="list-group-item">Late issues</a>
  <a href="#unassigned_issues" class="list-group-item">Open unassigned issues</a>
  <a href="#authors" class="list-group-item">Authors</a>
  </div>
  </div>
</div></div>

### <a name="quick-summary"></a>Quick Summary

There is a total of `r ncol(metrics)` metrics retrieved.

<div class="row"><div class="col-sm-3">
<span style="font-size:24pt"><span class="fa fa-bug"></span> </span>
</div><div class="col-sm-3">
<span><span style="font-size:24pt">``r metrics[['ITS_ISSUES_ALL']]``</span> issues total</span>
</div><div class="col-sm-3">
<span><span style="font-size:24pt">``r metrics[['ITS_ISSUES_LATE']]``</span> issues late</span>
</div><div class="col-sm-3">
<span><span style="font-size:24pt">``r metrics[['ITS_ISSUES_OPEN']]``</span> issues open</span>
</div></div>

<div class="row"><div class="col-sm-4">
<span style="font-size:24pt"><span class="fa fa-users"></span> </span>
</div><div class="col-sm-4">
<span><span style="font-size:24pt">``r metrics[['ITS_AUTHORS']]``</span> issue authors</span>
</div><div class="col-sm-4">
<span><span style="font-size:24pt">``r metrics[['ITS_PEOPLE']]``</span> people involved</span>
</div></div>

* Number of issues recently submitted: ``r metrics[['ITS_CREATED_1W']]`` last week, ``r metrics[['ITS_CREATED_1M']]`` last month, ``r metrics[['ITS_CREATED_1Y']]`` last year.
* The overall set of issues on this project has received ``r sum( issues[,c('user_notes_count')] )`` comments, ``r metrics[['ITS_TOTAL_UPVOTES']]`` upvotes and ``r metrics[['ITS_TOTAL_DOWNVOTES']]`` downvotes. 
* Total number of authors: ``r metrics[['ITS_AUTHORS']]`` overall, ``r metrics[['ITS_AUTHORS_1W']]`` last week, ``r metrics[['ITS_AUTHORS_1M']]`` last month, ``r metrics[['ITS_AUTHORS_1Y']]`` last year.
* Number of issues recently updated: ``r metrics[['ITS_CHANGED_1W']]`` last week, ``r metrics[['ITS_CHANGED_1M']]`` last month, ``r metrics[['ITS_CHANGED_1Y']]`` last year

```{r metrics_table, eval=F, echo=FALSE, message=FALSE, results='asis'}
t <- lapply(names(metrics), function(x) paste(x, ' <span class="badge">', metrics[[x]], '</span>, ', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```

The following plot uses [plotly services](http://plot.ly) to enable users to play with data itself, and its associated plot. Hover on the graph for more options.

<!-- iframe src="/projects/`r project.id`/EclipseIts/its_evol_summary.html" frameborder="0" style="width: 100%; height: 370px"></iframe -->

-----

### <a name="milestones"></a> Milestones

The following plots show the number of issues (opened, closed) on all active milestones for the project.

<div class="row">
```{r milestones_donuts, echo=FALSE, message=FALSE, results='asis'}
for (i in 1:nrow(milestones[milestones$state == 'active',])) {
  cat('<div class="col-md-3">')
  ms <- data.frame(unlist(c('issues_opened', 'issues_closed')), unlist(milestones[i,c('issues_opened', 'issues_closed')]))

  p <- gvisPieChart(ms,
                  options = list(
                    title=paste("Issues for milestone ", milestones[i,3], sep=""),
                    colors="['red', 'green']",
                    width=350, height=280,
                    pieHole= 0.4))

  print(p, 'chart')
  cat('</div>')
}
```
</div>


<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Active Milestones</div>

<table class="table table-striped">
  <tr><th>ID</th><th>IID</th><th>Title</th><th>Description</th><th>Issues (open/total)</th><th>Start date</th><th>Due date</th><th>Created</th><th>Updated</th></tr>
```{r milestones_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(milestones[milestones$state == 'active',], 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[2]], '</td><td>',
		           x[[3]], '</td><td>', x[[4]], '</td><td>', x[[11]], ' / ', x[[10]],
							 '</td><td>', x[[7]],'</td><td>', x[[6]], '</td><td>', x[[8]], 
							 '</td><td>', x[[9]], '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

-----

## <a name="late_issues"></a>Late issues

``r nrow(issues.late)`` issues have a past due date (compared to current time). Display is limited to 10 issues for readability.

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span>  Late issues</div>

<table class="table table-striped">
  <tr><th>ID</th><th>State</th><th>Title</th><th>Due</th><th>Created</th><th>Updated</th><th>Votes (up/down)</th><th>Comments</th></tr>
```{r builds_table, echo=FALSE, message=FALSE, results='asis'}
t <- apply(head(issues.late,10), 1, 
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[2]], '</td><td><a href="', 
							    x[[4]], '">', x[[3]], '</a></td><td>', x[[7]], '</td><td>', x[[5]], 
							    '</td><td>', x[[6]], '</td><td>', x[[8]], ' / ', x[[9]], '</td><td>', 
							    x[[10]], '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

-----

### <a name="unassigned_issues"></a>Open, unassigned issues

``r nrow(issues.unassigned.open)`` issues have an open status and are not yet assigned. Although it heavily depends on the issues workflow and local customs, it is generally considered good practice to assign issues when they are in an open state so as to know who is responsible for the action. Display is limited to 10 issues for readability.

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span>  Open, unassigned issues</div>

<table class="table table-striped">
  <tr><th>ID</th><th>State</th><th>Title</th><th>Due</th><th>Created</th><th>Updated</th><th>Votes (up/down)</th><th>Comments</th></tr>
```{r pipelines_table, echo=FALSE, message=FALSE, results='asis'}
t <- apply(head(issues.unassigned.open, 10), 1, 
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[2]], '</td><td><a href="', 
							    x[[4]], '">', x[[3]], '</a></td><td>', x[[7]], '</td><td>', x[[5]], 
							    '</td><td>', x[[6]], '</td><td>', x[[8]], ' / ', x[[9]], '</td><td>', 
							    x[[10]], '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

-----

### <a name="downloads"></a>Downloads

The visualisations on this page can be exported and easily reused on an external web site. You can find more information on iframes and pictures reuse in [the project&apos;s wiki](https://bitbucket.org/BorisBaldassari/alambic/wiki/Using_autogenerated_pictures/). Remember to change the server name in the code samples provided.

Plot of main evolution metrics of the issue tracking system

    <iframe src="http://server/projects/`r project.id`/EclipseIts/its_evol_summary.html" frameborder="0" style="width: 100%; height: 370px"></iframe>

Evolution of updates on issues

    <iframe src="http://server/projects/`r project.id`/EclipseIts/its_evol_changed.html" frameborder="0" style="width: 100%; height: 300px"></iframe>

Evolution of people involved in the issue tracking system

    <iframe src="http://server/projects/`r project.id`/EclipseIts/its_evol_people.html" frameborder="0" style="width: 100%; height: 300px"></iframe>
    
Evolution of opened and closed issues

    <iframe src="http://server/projects/`r project.id`/EclipseIts/its_evol_opened.html" frameborder="0" style="width: 100%; height: 300px"></iframe>

The visualisations used in this document rely on a number of flat CSV and JSON data files. You can download and play with them if you want to thereafter:

* List of raw static metrics retrieved from the eclipse dashboard [ <a href="import_its.json">Download JSON</a> ]
* List of computed static metrics for ITS [ <a href="metrics_its.csv">Download CSV</a> | <a href="metrics_its.json">Download JSON</a> ]
* List of evolution metrics for ITS [ <a href="metrics_evol_its.csv">Download CSV</a> | <a href="metrics_evol_its.json">Download JSON</a> ]


