---
#########################################################
#
# Copyright (c) 2015-2017 Castalia Solutions and others.
#
# All rights reserved. This program and the accompanying materials
# are made available under the terms of the Eclipse Public License v1.0
# which accompanies this distribution, and is available at
# http://www.eclipse.org/legal/epl-v10.html
#
# Contributors:
#   Boris Baldassari - Castalia Solutions
#
#########################################################

title: "Eclipse Forums"
author:
- name: "Boris Baldassari"
  affiliation: "Castalia Solutions"
output:
  html_fragment:
    toc: false
    fig_caption: true
    fig.width: 800
    self_contained: false
    lib_dir: libs
    echo: false
    dev: svg
---

```{r init, echo=FALSE, message=FALSE}
library(knitr)
require('ggplot2')
require('xtable')
require(xts)

#project.id <- 'technology.sisu'
# date.now <- '2016-03-17T15:38:55'
#date.before <- '2011-03-17T15:38:55'

opts_chunk$set(echo=F, message=F, warning=F, fig.path = paste(project.id, '_', sep=""))

file.forum.csv = paste("../../../../projects/", project.id, "/output/", project.id, '_eclipse_forums_forum.csv', sep="")
file.threads.csv = paste("../../../../projects/", project.id, "/output/", project.id, '_eclipse_forums_threads.csv', sep="")
file.posts.csv = paste("../../../../projects/", project.id, "/output/", project.id, '_eclipse_forums_posts.csv', sep="")

priority.colours <- c("#CC0000", "#DD5500", "#EEAA00", "#FFCC66")
binary.colours <- c("#325d88", "#d9534f") # "#325d88" green = #3e9c1a)

forum <- read.csv(file=file.forum.csv, header=TRUE)
threads <- read.csv(file=file.threads.csv, header=TRUE)
posts <- read.csv(file=file.posts.csv, header=TRUE)

forum$created.date <- as.POSIXct(forum$created_date, origin="1970-01-01")
threads$last.post.date <- as.POSIXct(threads$last_post_date, origin="1970-01-01")
posts$created.date <- as.POSIXct(posts$created_date, origin="1970-01-01")

posts.xts <- xts(posts, order.by = posts$created.date)
posts.xts.weekly <- apply.weekly(x=posts.xts, FUN = nrow)

# Paddle values, i.e. fill in empty dates
range <- range(posts.xts$created.date)
posts.xts.empty <- seq(from=as.Date(range[1]), to=as.Date(range[2]), by=7)
posts.xts.weekly <- merge(posts.xts.weekly, posts.xts.empty, all=TRUE)
posts.xts.weekly[is.na(posts.xts.weekly),] <- 0

```

<div class="row"><div class="col-lg-6">

## Forum summary

The Eclipse forge uses forums for user-level communication. The forum for project ``r forum$name`` can be found at ``r forum$html_url``. The list of threads can be found at ``r forum$topics_url``. 

Description of the forum:

> `r forum$description`

Main facts:

* Forum was created on ``r forum$created.date``.
* It is composed of a total of ``r forum$topic_count`` threads and ``r forum$post_count`` posts.
* Last post was made on ``r index(last(posts.xts))`` by user ``r forum$last_post_id`` and was about\\ ``r last(posts.xts)$subject``.
* Category of the forum is ``r forum$category_id`` ([see category](`r forum$category_url`)).

The wordcloud on the right details frequent words used in the question titles. The size and colour of the words depend on their number of appearances in questions. It shows what are the concerns and issues of people when dealing with the project.</p>

 </div><div class="col-lg-5">

 <img src="/projects/`r project.id`/EclipseForums/eclipse_forums_wordcloud.svg" frameborder="0" style="width: 100%; height: 370px" />

</div></div>

### Threads

<p>These are the 10 last active theads on the forums:</p>


```{r emls-recent-threads-list, results='asis'}
threads.table <- head(threads[,c('id', 'subject', 'last.post.date', 'last_post_id', 'replies', 'views')], 10)
threads.table$subject <- paste('<a href="', threads.table$html_url, '">', threads.table$subject, '</a>', sep='')
threads.table$last.post.date <- as.character(threads.table$last.post.date)
names(threads.table) <- c('ID', 'Subject', 'Last post date', 'Last post author', 'Replies', 'Views')

print(
    xtable(threads.table,
        caption = paste('10 last active threads on', project.id, 'forum.', sep=" "),
        digits=0, align="lllllll"), type="html",
    html.table.attributes='class="table table-striped"',
    caption.placement='bottom',
    include.rownames=FALSE,
    sanitize.text.function=function(x) { x }
)
#, align="lrrrrr", auto = TRUE
```



### Posts

<p>These are the 10 last sent posts on the forums:</p>


```{r emls-recent-posts-list, results='asis'}
posts.table <- head(posts[,c('id', 'subject', 'created.date', 'author_id')], 10)
posts.table$subject <- paste('<a href="', posts.table$html_url, '">', posts.table$subject, '</a>', sep='')
posts.table$created.date <- as.character(posts.table$created.date)
names(posts.table) <- c('ID', 'Subject', 'Post date', 'Post author')

print(
    xtable(head(posts.table, 10),
        caption = paste('10 most recent posts on', project.id, 'forum.', sep=" "),
        digits=0, align="lllll"), type="html",
    html.table.attributes='class="table table-striped"',
    caption.placement='bottom',
    include.rownames=FALSE,
    sanitize.text.function=function(x) { x }
)
```


<div class="row"><div class="col-lg-12">

### History of `r I(project.id)` questions

<iframe src="/projects/`r project.id`/EclipseForums/eclipse_forums_plot.html" frameborder="0" style="width: 100%; height: 320px"></iframe>

</div></div>
