---
#########################################################
#
# Copyright (c) 2015-2020 Castalia Solutions and others.
#
# All rights reserved. This program and the accompanying materials
# are made available under the terms of the Eclipse Public License v1.0
# which accompanies this distribution, and is available at
# http://www.eclipse.org/legal/epl-v10.html
#
# Contributors:
#   Boris Baldassari - Castalia Solutions
#
#########################################################

title: "GitHub Issues visualisation"
author:
- name: "Boris Baldassari"
  affiliation: Castalia Solutions
output:
  html_fragment:
    toc: false
    fig_caption: true
    fig.width: 800
    self_contained: false
    lib_dir: libs
    echo: false
    dev: svg
---

```{r init, echo=FALSE, message=FALSE}
library(knitr)
library(xts)
require('reshape2')
require(ggplot2)
require(xtable)

knitr::opts_chunk$set(fig.path = "figures/")

suppressPackageStartupMessages(library(googleVis))
options(gvis.plot.tag='chart')

# Enable font awesome
htmltools::tagList(rmarkdown::html_dependency_font_awesome())

# Plugin needs the following parameters:
#   * project.id
#   * github.user
#   * github.repo
#   * github.url

# project.id <- 'test.github.its'
# github.url <- 'https://api.github.com'
# github.user <- 'borisbaldassari'
# github.repo <- 'test'

plugin.id <- 'GitHubIts'
file.metrics = paste("../../../../projects/", project.id, "/output/", project.id, "_metrics_github_issues.csv", sep="")
file.info = paste("../../../../projects/", project.id, "/output/", project.id, "_info_github_issues.csv", sep="")
file.issues.all = paste("../../../../projects/", project.id, "/output/", project.id, "_github_issues.csv", sep="")
file.issues.open = paste("../../../../projects/", project.id, "/output/", project.id, "_github_issues_open.csv", sep="")

metrics <- read.csv(file=file.metrics, header=T)
info <- read.csv(file=file.info, header=T)
issues.all <- read.csv(file=file.issues.all, header=T)
issues.open <- read.csv(file=file.issues.open, header=T)

geticon <- function(value) {
  if (is.na(value)) { value <- FALSE }
  if (value == 1) {
    return('fa-check-square-o') 
  } else {
    return('fa-square-o') 
  }
}

issue_first <- head(issues.all[order(issues.all$created_at, decreasing = F),c('created_at')], n = 1)
issue_last <- head(issues.all[order(issues.all$updated_at, decreasing = T),c('updated_at')], n = 1)

```

## GitHub Issues `r github.user`/`r github.repo` 

<br />

<div class="row"><div class="col-sm-7">

github offers generic hosting services for software development. This plugin retrieves information about the project and its statistics, and computes metrics and recommendations. github offers a [complete API](https://docs.github.com/ee/api/README.html) to interact with a github server, and Perl has a ready-to-use [module that cover the API&apos;s features](http://search.cpan.org/~bluefeet/github-API-v3-0.08/lib/github/API/v3.pm).

Data for project is directly available from the project&apos;s dashboard:

* Project ID: `r github.user`/`r github.repo`
* Project URL: `r info['ITS_URL']` 

</div><div class="col-sm-4">
  <div class="panel panel-default">
  <div class="panel-heading"><h3 class="panel-title">Contents</h3></div>
  <div class="list-group">
  <a href="#summary" class="list-group-item">Quick Summary</a>
  <a href="#activity" class="list-group-item">Recent activity</a>
  <a href="#authors" class="list-group-item">Authors</a>
  <a href="#milestones" class="list-group-item">Milestones</a>
  </div>
  </div>
</div></div>

### <a name="quick-summary"></a>Quick Summary

The first issue was created on ``r issue_first`` and the last updated was made on ``r issue_last``.

<div class="row"><div class="col-sm-4">
<span><span style="font-size:24pt">``r trimws(metrics[['ITS_AUTHORS_1M']], which='both')``</span> Authors last month</span>
</div><div class="col-sm-4">
<span><span style="font-size:24pt">``r trimws(metrics[['ITS_CREATED_1M']], which='both')``</span> Created last month</span>
</div><div class="col-sm-4">
<span><span style="font-size:24pt">``r trimws(metrics[['ITS_UPDATED_1M']], which='both')``</span> Updated last month</span>
</div></div>

<div class="row"><div class="col-sm-4">
<span><span style="font-size:24pt">``r trimws(metrics[['ITS_ISSUES_OPEN']], which='both')``</span> Open issues</span>
</div><div class="col-sm-4">
<span><span style="font-size:24pt">``r trimws(metrics[['ITS_ISSUES_OPEN_OLD']], which='both')``</span> Old issues (not updated for more than 1 year)</span>
</div><div class="col-sm-4">
<span><span style="font-size:24pt">``r trimws(metrics[['ITS_ISSUES_OPEN_UNASSIGNED']], which='both')``</span> Open and Unassigned issues</span>
</div></div>

There is a total of ``r ncol(metrics)`` metrics retrieved.

```{r metrics_table, echo=FALSE, message=FALSE, results='asis'}
t <- lapply(names(metrics), function(x) paste(x, ' <span class="badge">', metrics[[x]], '</span>, ', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```

There is a total of ``r ncol(info)`` information retrieved:

```{r info_table, echo=FALSE, message=FALSE, results='asis'}
t <- lapply(names(info), function(x) paste('* ', x, ': ', info[[x]], "\n", sep=''))
t <- paste(t, collapse="")
cat(t)
```

-----

### <a name="activity"></a> Recent activity

* Number of issues recently submitted: ``r metrics[['ITS_CREATED_1W']]`` last week, ``r metrics[['ITS_CREATED_1M']]`` last month, ``r metrics[['ITS_CREATED_1Y']]`` last year.
* Total number of authors: ``r metrics[['ITS_AUTHORS']]`` overall, ``r metrics[['ITS_AUTHORS_1W']]`` last week, ``r metrics[['ITS_AUTHORS_1M']]`` last month, ``r metrics[['ITS_AUTHORS_1Y']]`` last year.
* Number of issues recently updated: ``r metrics[['ITS_UPDATED_1W']]`` last week, ``r metrics[['ITS_UPDATED_1M']]`` last month, ``r metrics[['ITS_UPDATED_1Y']]`` last year.

-----

<div class="row">
<div class="col-md-6">

### <a name="authors"></a> Authors

The following authors have been found in the Git repository, sorted by lines count:

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Authors</div>

<table class="table table-striped">
  <tr><th>Authors</th><th>Lines Count</th></tr>
```{r authors_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
authors <- table(issues.all$creator)
authors <- as.data.frame(x = table(issues.all$creator))

t <- apply(authors[order(authors$Freq, decreasing = T),], 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[2]], '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

</div>
<div class="col-md-6">
  <iframe src="/projects/`r project.id`/GitHubIts/github_issues_authors_pie.html" frameborder="0" style="width: 500px; height: 340px"></iframe>
</div>
</div>

-----

### <a name="milestones"></a> Milestones

The following plots show the number of issues (opened, closed) on all the milestones of the project that have at least one open task.

<div class="row">
```{r milestones_donuts, echo=FALSE, message=FALSE, results='asis'}
milestones <- data.frame(Milestone=unique(issues.all$milestone), Open=0, Closed=0, All=0);
milestones <- milestones[order(milestones$Milestone, decreasing = T),]

for (i in 1:nrow(milestones)) { #[seq(1,8),]
  issues.m <- issues.all[issues.all$milestone == milestones[i,1],]
  issues.m.opened <- nrow(issues.m[issues.m$status == 'open',])
  issues.m.closed <- nrow(issues.m[issues.m$status != 'open',])

  milestones[i,c('Open')] <- issues.m.opened
  milestones[i,c('Closed')] <- issues.m.closed

  ms <- data.frame(unlist(c('issues_opened', 'issues_closed')), unlist(c(issues.m.opened, issues.m.closed)))

  # We want to display only milestones with open tasks.
  if(issues.m.opened == 0) { next }

  cat('<div class="col-md-3">')
  p <- gvisPieChart(ms,
                  options = list(
                    title=paste("Issues for milestone ", milestones[i,1], sep=""),
                    colors="['red', 'green']",
                    width=350, height=280,
                    pieHole= 0.4))

  print(p, 'chart')
  cat('</div>')
}
```
</div>

The complete list of milestones is provided below:

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Milestones</div>

<table class="table table-striped">
  <tr><th>Name</th><th>Issues total</th><th>Issues opened</th><th>Issues closed</th></tr>
```{r milestones_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
milestones$All <- milestones$Open + milestones$Closed
milestones <- milestones[order(milestones$Milestone, decreasing = T),]
t <- apply(milestones[order(milestones$Milestone, decreasing = T),], 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', trimws(x[[4]], which='both'), '</td><td>',
		           trimws(x[[2]], which='both'), '</td><td>', trimws(x[[3]], which='both'), '</td></tr>', sep=''))
t <- paste(t, collapse="")
cat(t)
```
</table>
</div>
