---
title: "Eclipse ITS visualisation"
author:
- name: "Boris Baldassari"
  affiliation: Castalia Solutions
output:
  html_fragment:
    toc: false
    fig_caption: true
    fig.width: 800
    self_contained: false
    lib_dir: libs
    echo: false
    dev: svg
---

```{r init, echo=FALSE, message=FALSE}

library(knitr)
library(xts)
library(reshape2)
require(ggplot2)
require(xtable)

knitr::opts_chunk$set(fig.path = "figures/")

#project.id <- 'modeling.sirius'
plugin.id <- 'EclipseIts'
file.static = paste("", project.id, "_its.csv", sep="")
file.evol = paste("", project.id, "_its_evol.csv", sep="")

metrics <- read.csv(file=file.static, header=T)
evol <- read.csv(file=file.evol, header=T)

```

## Eclipse Issue Tracking System

<br />

<div class="row"><div class="col-sm-7">

The official Eclipse Issue Tracking System (ITS) is Bugzilla, hosted at http://bugs.eclipse.org . Some projects however use a mix of GitHub and the Eclipse forge to manage the various repositories, and may use the GitHub ITS. 

Bugzilla itself has some reporting capabilities, available through its web interface. For more elaborated plots and numbers, the Eclipse Foundations has setup a dedicated server to analyse project repositories at http://dashboard.eclipse.org , powered by the [MetricsGrimoire](https://metricsgrimoire.github.io/) suite developed by [Bitergia](http://bitergia.com).

Data for project is directly available from the project&apos;s dashboard:

* project summary: http://dashboard.eclipse.org/project.html?project=`r project.id`, 
* as JSON files: http://dashboard.eclipse.org/data/json/`r project.id`.

</div><div class="col-sm-4">
  <div class="panel panel-default">
  <div class="panel-heading"><h3 class="panel-title">Contents</h3></div>
  <div class="list-group">
  <a href="#summary" class="list-group-item">Quick Summary</a>
  <a href="#changed" class="list-group-item">Changed bugs</a>
  <a href="#people" class="list-group-item">People</a>
  <a href="#opened-closed" class="list-group-item">Opened vs Closed</a>
  <a href="#downloads" class="list-group-item">Downloads</a>
  </div>
  </div>
</div></div>

### <a name="quick-summary"></a>Quick Summary

``r ncol(metrics)`` static metrics relative to the current project&apos;s state have been retrieved from the Eclipse dashboard:

```{r metrics_table, echo=FALSE, message=FALSE, results='asis'}
t <- lapply(names(metrics), function(x) paste(x, ' <span class="badge">', metrics[[x]], '</span>, ', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```

The evolution of ``r ncol(evol)`` metrics has been retrieved, spaning from ``r evol[1,1]`` to ``r evol[nrow(evol),1]``: ``r paste(names(evol), collapse=", ")``

The following plot uses [plotly services](http://plot.ly) to enable users to play with data itself, and its associated plot. Hover on the graph for more options.

<iframe src="/projects/`r project.id`/EclipseIts/its_evol_summary.html" frameborder="0" style="width: 100%; height: 370px"></iframe>

-----

### <a name="changed"></a>Changed bugs

The following plot shows the evolution of the [number of updates](/documentation/metrics#ITS_CHANGED) on issues during the overall time range covered by the analysis. Updates include opening, closing, changing state or adding information to the issue and denotes the activity of the project on the issue tracking system.

<div class="row"><div class="col-md-12">

<iframe src="/projects/`r project.id`/EclipseIts/its_evol_changed.html" frameborder="0" style="width: 100%; height: 300px"></iframe>

</div></div>

-----

### <a name="people"></a>People

The following plot shows the evolution of [changers](/documentation/metrics#ITS_CHANGED), [openers](/documentation/metrics#ITS_OPENERS) and [closers](/documentation/metrics#ITS_CLOSERS) of issues during the overall time range covered by the analysis. 

<iframe src="/projects/`r project.id`/EclipseIts/its_evol_people.html" frameborder="0" style="width: 100%; height: 300px"></iframe>

-----

### <a name="opened-closed"></a>Opened vs Closed

The following plot shows the evolution of the number of issues [opened](/documentation/metrics#ITS_OPENED) and [closed](/documentation/metrics#ITS_CLOSED) per week. These numbers are a good indicators both of the activity of the project on the issue tracking system and the diversity of its actors.

<iframe src="/projects/`r project.id`/EclipseIts/its_evol_opened.html" frameborder="0" style="width: 100%; height: 300px"></iframe>

-----

### <a name="downloads"></a>Downloads

The visualisations on this page can be exported and easily reused on an external web site. You can find more information on iframes and pictures reuse in [the project&apos;s wiki](https://bitbucket.org/BorisBaldassari/alambic/wiki/Using_autogenerated_pictures/). Remember to change the server name in the code samples provided.

Plot of main evolution metrics of the issue tracking system

    <iframe src="http://server/projects/`r project.id`/EclipseIts/its_evol_summary.html" frameborder="0" style="width: 100%; height: 370px"></iframe>

Evolution of updates on issues

    <iframe src="http://server/projects/`r project.id`/EclipseIts/its_evol_changed.html" frameborder="0" style="width: 100%; height: 300px"></iframe>

Evolution of people involved in the issue tracking system

    <iframe src="http://server/projects/`r project.id`/EclipseIts/its_evol_people.html" frameborder="0" style="width: 100%; height: 300px"></iframe>
    
Evolution of opened and closed issues

    <iframe src="http://server/projects/`r project.id`/EclipseIts/its_evol_opened.html" frameborder="0" style="width: 100%; height: 300px"></iframe>

The visualisations used in this document rely on a number of flat CSV and JSON data files. You can download and play with them if you want to thereafter:

* List of raw static metrics retrieved from the eclipse dashboard [ <a href="import_its.json">Download JSON</a> ]
* List of computed static metrics for ITS [ <a href="metrics_its.csv">Download CSV</a> | <a href="metrics_its.json">Download JSON</a> ]
* List of evolution metrics for ITS [ <a href="metrics_evol_its.csv">Download CSV</a> | <a href="metrics_evol_its.json">Download JSON</a> ]


