---
title: "SonarQube 4.5.x"
author:
- name: "Boris Baldassari"
  affiliation: Castalia Solutions
output:
  html_fragment:
    toc: false
    fig_caption: true
    fig.width: 800
    self_contained: false
    lib_dir: libs
    echo: false
    dev: svg
---

```{r init, echo=FALSE, message=FALSE}

library(knitr)
require(ggplot2)
require(xtable)

opts_chunk$set(fig.width=5, fig.height=5, echo=F, fig.path = 'figures/')

project.id <- "modeling.gendoc"
plugin.id <- "Scancode"
file.metrics <- paste("../../../../projects/", project.id, "/output/", project.id, "_scancode_metrics.csv", sep="")
file.authors <- paste("../../../../projects/", project.id, "/output/", project.id, "_scancode_authors.csv", sep="")
file.copyrights <- paste("../../../../projects/", project.id, "/output/", project.id, "_scancode_copyrights.csv", sep="")
file.files <- paste("../../../../projects/", project.id, "/output/", project.id, "_scancode_files.csv", sep="")
file.holders <- paste("../../../../projects/", project.id, "/output/", project.id, "_scancode_holders.csv", sep="")
file.licences<- paste("../../../../projects/", project.id, "/output/", project.id, "_scancode_licences.csv", sep="")
file.programming_languages <- paste("../../../../projects/", project.id, "/output/", project.id, "_scancode_programming_languages.csv", sep="")

abc <- c('A', 'B', 'C', 'D', 'E', 'F', 'G')

metrics <- read.csv(file=file.metrics, header=T)
authors <- read.csv(file=file.authors, header=T)
copyrights <- read.csv(file=file.copyrights, header=T)
files <- read.csv(file=file.files, header=T)
holders <- read.csv(file=file.holders, header=T)
licences <- read.csv(file=file.licences, header=T)
programming_languages <- read.csv(file=file.programming_languages, header=T)

dir_vol <- metrics[metrics$metric == 'SC_FILES_VOL',2] - metrics[metrics$metric == 'SC_FILES_COUNT',2]
#issues <- merge(issues.blocker, issues.critical, all=TRUE)
#issues <- merge(issues, issues.major, all=TRUE)

#violations <- as.data.frame(t(sq.metrics[,c('SQ_VIOLATIONS_BLOCKER', 'SQ_VIOLATIONS_CRITICAL', 'SQ_VIOLATIONS_MAJOR', 'SQ_VIOLATIONS_MINOR', 'SQ_VIOLATIONS_INFO')]))
#violations$names <- rownames(violations)
#names(violations) <- c('Values', 'Severity')
```

## Scancode results analysis for `r I(project.id)`

<br />

<div class="row"><div class="col-sm-7">

[Scancode toolkit](https://github.com/nexB/scancode-toolkit) is an open-source tool that detects licenses, copyrights, package manifests and dependencies by scanning a codebase. 

You can learn more about this module on its [documentation page](http://alambic.io/Plugins/Pre/Scancode.html) on the project wiki.

</div><div class="col-sm-4">
  <div class="panel panel-default">
  <div class="panel-heading"><h3 class="panel-title">Contents</h3></div>
  <div class="list-group">
  <a href="#metrics" class="list-group-item">Metrics</a>
  <a href="#issues" class="list-group-item">Violations</a>
  <a href="#downloads" class="list-group-item">Downloads</a>
  </div>
  </div>
</div></div>

-----

### <a name="metrics"></a>Metrics

<div class="row"><div class="col-sm-6">

Scancode identified ``r nrow(metrics)`` metrics:

* A total of ``r metrics[metrics$metric == 'SC_FILES_VOL',2]`` entries in the codebase, including ``r metrics[metrics$metric == 'SC_FILES_COUNT',2]`` files and ``r dir_vol`` directories,
* *Key files* are top-level codebase files such as COPYING, README and package manifests. Current codebase includes ``r  metrics[metrics$metric == 'SC_KEY_FILES',2]`` key files, and ``r metrics[metrics$metric == 'SC_GENERATED_VOL',2]`` files considered as generated.

* Total number of licences identified is ``r metrics[metrics$metric == 'SC_LICENSES_VOL',2]``.
* Total number of copyrights identified is ``r metrics[metrics$metric == 'SC_COPYRIGHTS_VOL',2]``.
* Total number of holders identified is ``r metrics[metrics$metric == 'SC_HOLDERS_VOL',2]``.
* Total number of authors identified is ``r metrics[metrics$metric == 'SC_AUTHORS_VOL',2]``.
* Total number of programming languages identified is ``r metrics[metrics$metric == 'SC_PROGS_VOL',2]``.


</div><div class="col-sm-6">

</div></div>

-----

### <a name="licences"></a>Licences

<div class="row"><div class="col-sm-6">

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Licences</div>

<table class="table table-striped">
  <tr><th>Licence</th><th>Count</th></tr>
```{r licences_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(licences, 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[2]], '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

</div><div class="col-sm-6">

<iframe src="/projects/`r project.id`/Scancode/scancode_licences.html" frameborder="0" style="width: 100%; height: 360px"></iframe>

</div></div>

----

### <a name="copyrights"></a>Copyrights

<div class="row"><div class="col-sm-6">

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Copyrights</div>

<table class="table table-striped">
  <tr><th>Copyright</th><th>Count</th></tr>
```{r copyrights_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(copyrights, 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[2]], '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

</div><div class="col-sm-6">

<iframe src="/projects/`r project.id`/Scancode/scancode_copyrights.html" frameborder="0" style="width: 100%; height: 360px"></iframe>

</div></div>

----

### <a name="authors"></a>Authors

<div class="row"><div class="col-sm-6">

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Authors</div>

<table class="table table-striped">
  <tr><th>Author</th><th>Count</th></tr>
```{r authors_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(authors, 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[2]], '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

</div><div class="col-sm-6">

<iframe src="/projects/`r project.id`/Scancode/scancode_authors.html" frameborder="0" style="width: 100%; height: 360px"></iframe>

</div></div>

----

### <a name="holders"></a>Holders

<div class="row"><div class="col-sm-6">

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Holders</div>

<table class="table table-striped">
  <tr><th>Holder</th><th>Count</th></tr>
```{r authors_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(holders, 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[2]], '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

</div><div class="col-sm-6">

<iframe src="/projects/`r project.id`/Scancode/scancode_holders.html" frameborder="0" style="width: 100%; height: 360px"></iframe>

</div></div>

----

### <a name="langs"></a>Programming Languages

<div class="row"><div class="col-sm-6">

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Programming Languages</div>

<table class="table table-striped">
  <tr><th>Programming Language</th><th>Count</th></tr>
```{r authors_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(programming_languages, 1,
		   function(x) paste(' <tr><td>', x[[1]], '</td><td>', x[[2]], '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

</div><div class="col-sm-6">

<iframe src="/projects/`r project.id`/Scancode/scancode_programming_languages.html" frameborder="0" style="width: 100%; height: 360px"></iframe>

</div></div>

-----

### <a name="downloads"></a>Downloads

The visualisations on this page can be exported and easily reused on an external web site. You can find more information on iframes and pictures reuse in [the project&apos;s wiki](https://alambic.io/Documentation/Basics/Exports.html). Remember to change the server name in the code samples provided.

Pie chart of licences (HTML)

    <iframe src="http://server/projects/`r project.id`/Scancode/scancode_licences.html" frameborder="0" style="width: 100%; height: 350px"></iframe>

Pie chart of copyrights (HTML)

    <iframe src="http://server/projects/`r project.id`/Scancode/scancode_copyrights.html" frameborder="0" style="width: 100%; height: 350px"></iframe>

Pie chart of authors (HTML)

    <iframe src="http://server/projects/`r project.id`/Scancode/scancode_authors.html" frameborder="0" style="width: 100%; height: 350px"></iframe>

Pie chart of holders (HTML)

    <iframe src="http://server/projects/`r project.id`/Scancode/scancode_holders.html" frameborder="0" style="width: 100%; height: 350px"></iframe>

Pie chart of programming languages (HTML)

    <iframe src="http://server/projects/`r project.id`/Scancode/scancode_programming_languages.html" frameborder="0" style="width: 100%; height: 350px"></iframe>

