---
title: "SonarQube 4.5.x"
author:
- name: "Boris Baldassari"
  affiliation: Castalia Solutions
output:
  html_fragment:
    toc: false
    fig_caption: true
    fig.width: 800
    self_contained: false
    lib_dir: libs
    echo: false
    dev: svg
---

```{r init, echo=FALSE, message=FALSE, warning=FALSE}

library(knitr)
require(ggplot2)
require(xtable)

opts_chunk$set(fig.width=5, fig.height=5, echo=F, fig.path = 'figures/')

#project.id <- "modeling.sirius"
#project.id <- "modeling.gendoc"
plugin.id <- "Scancode"
file.metrics <- paste("../../../../projects/", project.id, "/output/", project.id, "_metrics_scancode.csv", sep="")
file.specials <- paste("../../../../projects/", project.id, "/output/", project.id, "_scancode_special_files.csv", sep="")
file.authors <- paste("../../../../projects/", project.id, "/output/", project.id, "_scancode_authors.csv", sep="")
file.copyrights <- paste("../../../../projects/", project.id, "/output/", project.id, "_scancode_copyrights.csv", sep="")
file.files <- paste("../../../../projects/", project.id, "/output/", project.id, "_scancode_files.csv", sep="")
file.holders <- paste("../../../../projects/", project.id, "/output/", project.id, "_scancode_holders.csv", sep="")
file.licences<- paste("../../../../projects/", project.id, "/output/", project.id, "_scancode_licences.csv", sep="")
file.programming_languages <- paste("../../../../projects/", project.id, "/output/", project.id, "_scancode_programming_languages.csv", sep="")

abc <- c('A', 'B', 'C', 'D', 'E', 'F', 'G')

metrics <- read.csv(file=file.metrics, header=T)
specials <- read.csv(file=file.specials, header=T)
authors <- read.csv(file=file.authors, header=T)
copyrights <- read.csv(file=file.copyrights, header=T)
files <- read.csv(file=file.files, header=T)
holders <- read.csv(file=file.holders, header=T)
licences <- read.csv(file=file.licences, header=T)
programming_languages <- read.csv(file=file.programming_languages, header=T)

dir_vol <- metrics[metrics$metric == 'SC_FILES_VOL',2] - metrics[metrics$metric == 'SC_FILES_COUNT',2]
sc_files_vol <- metrics[metrics$metric == 'SC_FILES_VOL',2]
```

## Scancode analysis results  for `r I(project.id)`

<br />

<div class="row"><div class="col-sm-7">

[Scancode toolkit](https://github.com/nexB/scancode-toolkit) is an open-source tool that detects licenses, copyrights, package manifests and dependencies by scanning a codebase. 

You can learn more about this module on its [documentation page](http://alambic.io/Plugins/Pre/Scancode.html) on the project wiki.

### <a name="metrics"></a>Metrics

Scancode identified ``r nrow(metrics)`` metrics:

* A total of ``r sc_files_vol`` entries in the codebase, including ``r metrics[metrics$metric == 'SC_FILES_COUNT',2]`` files and ``r dir_vol`` directories,
* Current codebase includes ``r  metrics[metrics$metric == 'SC_SPECIAL_FILES',2]`` special files, and ``r metrics[metrics$metric == 'SC_GENERATED_VOL',2]`` files considered as generated.

* Total number of licences identified is ``r metrics[metrics$metric == 'SC_LICENSES_VOL',2]``.
* Total number of copyrights identified is ``r metrics[metrics$metric == 'SC_COPYRIGHTS_VOL',2]``.
* Total number of holders identified is ``r metrics[metrics$metric == 'SC_HOLDERS_VOL',2]``.
* Total number of authors identified is ``r metrics[metrics$metric == 'SC_AUTHORS_VOL',2]``.
* Total number of programming languages identified is ``r metrics[metrics$metric == 'SC_PROGS_VOL',2]``.


</div><div class="col-sm-4">
  <div class="panel panel-default">
  <div class="panel-heading"><h3 class="panel-title">Contents</h3></div>
  <div class="list-group">
  <a href="#metrics" class="list-group-item">Metrics</a>
  <a href="#specialfiles" class="list-group-item">Special files</a>
  <a href="#licences" class="list-group-item">Liences</a>
  <a href="#copyrights" class="list-group-item">Copyrights</a>
  <a href="#authors" class="list-group-item">Authors</a>
  <a href="#holders" class="list-group-item">Holders</a>
  <a href="#langs" class="list-group-item">Programming languages</a>
  <a href="#downloads" class="list-group-item">Downloads</a>
  </div>
  </div>
</div></div>

-----

### <a name="specialfiles"></a>Special files

*Special files* are defined as:

* key files: top-level codebase files such as COPYING, README and package manifests. 
* readmes 
* legal stuff files, eg licences
* manifests
  
The following table shows the list of special files identified in the codebase (only the 10 first items are displayed). You can download the full list of special files from [here](/projects/`r project.id`/Scancode/scancode_special_files.csv).

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Key files</div>

<table class="table table-striped">
  <tr><th>File path</th><th>Type</th></tr>
```{r keyfiles_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(specials[seq(1,10),], 1,
		   function(x) paste(' <tr><td>', trimws(x[[1]]), '</td><td>', trimws(x[[2]]), '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div> 

----

### <a name="licences"></a>Licences

The full list of licences can be downloaded from [here](/projects/`r project.id`/Scancode/scancode_licences.csv).

<div class="row"><div class="col-sm-6">

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Licences</div>

<table class="table table-striped">
  <tr><th>Licence</th><th>Count</th></tr>
```{r licences_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(licences, 1,
		   function(x) paste(' <tr><td>', trimws(x[[1]]), '</td><td>', trimws(x[[2]]), '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

</div><div class="col-sm-6">

<iframe src="/projects/`r project.id`/Scancode/scancode_licences.html" frameborder="0" style="width: 100%; height: 360px"></iframe>

</div></div>

----

### <a name="copyrights"></a>Copyrights

The full list of copyrights can be downloaded from [here](/projects/`r project.id`/Scancode/scancode_copyrights.csv).

<div class="row"><div class="col-sm-6">

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Copyrights</div>

<table class="table table-striped">
  <tr><th>Copyright</th><th>Count</th></tr>
```{r copyrights_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(copyrights, 1,
		   function(x) paste(' <tr><td>', trimws(x[[1]]), '</td><td>', trimws(x[[2]]), '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

</div><div class="col-sm-6">

<iframe src="/projects/`r project.id`/Scancode/scancode_copyrights.html" frameborder="0" style="width: 100%; height: 360px"></iframe>

</div></div>

----

### <a name="authors"></a>Authors

The full list of authors can be downloaded from [here](/projects/`r project.id`/Scancode/scancode_authors.csv).

<div class="row"><div class="col-sm-6">

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Authors</div>

<table class="table table-striped">
  <tr><th>Author</th><th>Count</th></tr>
```{r authors_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(authors, 1,
		   function(x) paste(' <tr><td>', trimws(x[[1]]), '</td><td>', trimws(x[[2]]), '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

</div><div class="col-sm-6">

<iframe src="/projects/`r project.id`/Scancode/scancode_authors.html" frameborder="0" style="width: 100%; height: 360px"></iframe>

</div></div>

----

### <a name="holders"></a>Holders

The full list of holders can be downloaded from [here](/projects/`r project.id`/Scancode/scancode_holders.csv).

<div class="row"><div class="col-sm-6">

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Holders</div>

<table class="table table-striped">
  <tr><th>Holder</th><th>Count</th></tr>
```{r holders_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(holders, 1,
		   function(x) paste(' <tr><td>', trimws(x[[1]]), '</td><td>', trimws(x[[2]]), '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

</div><div class="col-sm-6">

<iframe src="/projects/`r project.id`/Scancode/scancode_holders.html" frameborder="0" style="width: 100%; height: 360px"></iframe>

</div></div>

----

### <a name="langs"></a>Programming Languages

The full list of programming languages can be downloaded from [here](/projects/`r project.id`/Scancode/scancode_programming_languages.csv).

<div class="row"><div class="col-sm-6">

<div class="panel panel-default">
<div class="panel-heading" style="background-color: #3E3F3A; color: white"><span class="fa fa-indent"></span> Programming Languages</div>

<table class="table table-striped">
  <tr><th>Programming Language</th><th>Count</th></tr>
```{r lang_table, eval=T, echo=FALSE, message=FALSE, results='asis'}
t <- apply(programming_languages, 1,
		   function(x) paste(' <tr><td>', trimws(x[[1]]), '</td><td>', trimws(x[[2]]), '</td></tr>', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```
</table>
</div>

</div><div class="col-sm-6">

<iframe src="/projects/`r project.id`/Scancode/scancode_programming_languages.html" frameborder="0" style="width: 100%; height: 360px"></iframe>

</div></div>

-----

### <a name="downloads"></a>Downloads

The visualisations on this page can be exported and easily reused on an external web site. You can find more information on iframes and pictures reuse in [the project&apos;s wiki](https://alambic.io/Documentation/Basics/Exports.html). Remember to change the server name in the code samples provided.

Pie chart of licences (HTML)

```
    <iframe src="http://server/projects/`r project.id`/Scancode/scancode_licences.html" frameborder="0" style="width: 100%; height: 350px"></iframe>
```

Pie chart of copyrights (HTML)

```
    <iframe src="http://server/projects/`r project.id`/Scancode/scancode_copyrights.html" frameborder="0" style="width: 100%; height: 350px"></iframe>
```

Pie chart of authors (HTML)

```
    <iframe src="http://server/projects/`r project.id`/Scancode/scancode_authors.html" frameborder="0" style="width: 100%; height: 350px"></iframe>
```

Pie chart of holders (HTML)

```
    <iframe src="http://server/projects/`r project.id`/Scancode/scancode_holders.html" frameborder="0" style="width: 100%; height: 350px"></iframe>
```

Pie chart of programming languages (HTML)

```
    <iframe src="http://server/projects/`r project.id`/Scancode/scancode_programming_languages.html" frameborder="0" style="width: 100%; height: 350px"></iframe>
```

