---
title: "Eclipse MLS visualisation"
author:
- name: "Boris Baldassari"
  affiliation: Castalia Solutions
output:
  html_fragment:
    toc: false
    fig_caption: true
    fig.width: 800
    self_contained: false
    lib_dir: libs
    echo: false
    dev: svg
---

```{r init, echo=FALSE, message=FALSE}
project.id <- 'modeling.sirius'
plugin.id <- 'eclipse_mls'
file.static = paste("", project.id, "_mls.csv", sep="")
file.evol = paste("", project.id, "_mls_evol.csv", sep="")

library(knitr)
library(xts)
library(reshape2)

knitr::opts_chunk$set(fig.path = paste( 'figures/', plugin.id, '/', project.id, '/', sep=""))
#opts_knit$set(progress = TRUE, verbose = TRUE, self.contained=T)

require(ggplot2)
require(xtable)

metrics <- read.csv(file=file.static, header=T)
evol <- read.csv(file=file.evol, header=T)
url <- paste('http://dashboard.eclipse.org/data/json/', project.id, '-mls-prj-static.json', sep='');
```

## Eclipse Mailing List System

<br />

<div class="row"><div class="col-sm-7">

The official Eclipse developer mailing lists are hosted on (https://dev.eclipse.org/mailman/listinfo) and use Mailman. User communications are achieved through forums, hosted at (http://www.eclipse.org/forums/?). Both are analysed together and made available on [the Eclipse dashboard](http://dashboard.eclipse.org):

* project summary: http://dashboard.eclipse.org/project.html?project=`r project.id`, 
* as JSON files: http://dashboard.eclipse.org/data/json/`r project.id`.

</div><div class="col-sm-4">
  <div class="panel panel-default">
  <div class="panel-heading"><h3 class="panel-title">Contents</h3></div>
  <div class="list-group">
  <a href="#summary" class="list-group-item">Quick Summary</a>
  <a href="#changed" class="list-group-item">Sent emails</a>
  <a href="#people" class="list-group-item">People</a>
  <a href="#downloads" class="list-group-item">Downloads</a>
  </div>
  </div>
</div></div>

### <a name="quick-summary"></a>Quick Summary

``r ncol(metrics)`` static metrics relative to the current project&apos;s state have been retrieved from the Eclipse dashboard:

```{r metrics_table, echo=FALSE, message=FALSE, results='asis'}
t <- lapply(names(metrics), function(x) paste(x, ' <span class="badge">', metrics[[x]], '</span>, ', sep=''))
t <- paste(t, collapse=" ")
cat(t)
```

The evolution of ``r ncol(evol)`` metrics has been retrieved, spaning from ``r evol[1,1]`` to ``r evol[nrow(evol),1]``: ``r paste(names(evol), collapse=", ")``

The following plot uses [plotly services](http://plot.ly) to enable users to play with data itself, and its associated plot. Hover on the graph for more options.

<iframe src="/projects/`r project.id`/EclipseMls/mls_evol_summary.html" frameborder="0" style="width: 100%; height: 370px"></iframe>

### Sent emails

The following plot shows the evolution of [sent emails](/documentation/metrics#MLS_SENT), [threads](/documentation/metrics#MLS_THREADS) and [responses](/documentation/metrics#MLS_SENT_RESPONSE) during the overall time range covered by the analysis. 

<iframe src="/projects/`r project.id`/EclipseMls/mls_evol_sent.html" frameborder="0" style="width: 100%; height: 300px"></iframe>

### People

The following plot shows the evolution of [overall senders](/documentation/metrics#MLS_SENDERS), [threads openers (senders init)](/documentation/metrics#ITS_OPENERS) and [answerers (senders response)](/documentation/metrics#ITS_CLOSERS) on mailing lists and forums during the overall time range covered by the analysis. 

<iframe src="/projects/`r project.id`/EclipseMls/mls_evol_people.html" frameborder="0" style="width: 100%; height: 300px"></iframe>



-----

### <a name="downloads"></a>Downloads

The visualisations on this page can be exported and easily reused on an external web site. You can find more information on iframes and pictures reuse in [the project&apos;s wiki](https://bitbucket.org/BorisBaldassari/alambic/wiki/Using_autogenerated_pictures/). Remember to change the server name in the code samples provided.

Plot of main evolution metrics of the mailing lists and forums

    <iframe src="http://server/projects/`r project.id`/EclipseMls/mls_evol_summary.html" frameborder="0" style="width: 100%; height: 370px"></iframe>

Evolution of sent emails

    <iframe src="http://server/projects/`r project.id`/EclipseIts/mls_evol_changed.html" frameborder="0" style="width: 100%; height: 300px"></iframe>

Evolution of people involved in the mailing lists and forums

    <iframe src="http://server/projects/`r project.id`/EclipseIts/its_evol_people.html" frameborder="0" style="width: 100%; height: 300px"></iframe>

The visualisations used in this document rely on a number of flat CSV and JSON data files. You can download and play with them if you want to thereafter:

* List of raw static metrics retrieved from the eclipse dashboard [ <a href="import_mls.json">Download JSON</a> ]
* List of computed static metrics for ITS [ <a href="metrics_mls.csv">Download CSV</a> | <a href="metrics_mls.json">Download JSON</a> ]
* List of evolution metrics for MLS [ <a href="metrics_evol_mls.csv">Download CSV</a> | <a href="metrics_evol_mls.json">Download JSON</a> ]


