  ---
#########################################################
#
# Copyright (c) 2015-2017 Castalia Solutions and others.
#
# All rights reserved. This program and the accompanying materials
# are made available under the terms of the Eclipse Public License v1.0
# which accompanies this distribution, and is available at
# http://www.eclipse.org/legal/epl-v10.html
#
# Contributors:
#   Boris Baldassari - Castalia Solutions
#
#########################################################

title: "Alambic -- R analysis document"
author: "Boris Baldassari"
output:
  pdf_document:
    toc: true
    toc_depth: 3
---


```{r init, echo=FALSE, message=FALSE}
library(xts)
library(ggplot2)
require(xtable)

knitr::opts_chunk$set(
  fig.align = 'center',
  warning=FALSE,
  error=TRUE,
  echo=FALSE,
  message=FALSE,
  progress = TRUE)

#project.id <- 'test.project'

file.metrics <- paste("../../../../projects/", project.id, "/output/",
 project.id, "_metrics.csv", sep="")
metrics <- read.csv(file=file.metrics, header=T)

file.indics <- paste("../../../../projects/", project.id, "/output/",
 project.id, "_indics.csv", sep="")
indics <- read.csv(file=file.indics, header=T)

file.attributes <- paste("../../../../projects/", project.id, "/output/",
 project.id, "_attributes.csv", sep="")
attributes <- read.csv(file=file.attributes, header=T)

file.metrics_ref <- paste("../../../../projects/", project.id, "/output/",
 project.id, "_metrics_ref.csv", sep="")
metrics_ref <- read.csv(file=file.metrics_ref, header=T)

file.attrs_ref <- paste("../../../../projects/", project.id, "/output/",
 project.id, "_attrs_ref.csv", sep="")
attrs_ref <- read.csv(file=file.attrs_ref, header=T)
```

# Summary

This plugin generates a PDF document with information about project **`r project.id`**.

This plugin is intended as an example of [R Markdown document](http://rmarkdown.rstudio.com/) to help people easily setup their own R analysis on software development data.


# Metrics

\begin{centering}

```{r table_metrics, results='asis', echo=FALSE}
print( xtable( metrics, 
       align="|c|p{5cm}|p{3cm}|"), comment=FALSE,
       include.rownames=FALSE, include.colnames=TRUE, 
       floating=FALSE, size="\\scriptsize" )
```

\end{centering}

```{r metrics_list, results='asis', echo=FALSE}
f_m <- function(x, output) {
  name <- paste("\n\n## ", x[2], sep=" ")
  id <- paste("ID: ", x[1], sep=" ")
  if ( sum(indics[,1]==x[1]) ) {
    value <- paste("Value: ", metrics[metrics[,1]==x[1], 2], 
      " ( ", indics[indics[,1]==x[1], 2], " / 5 ) ", sep="")
  } else {
    value <- paste("Value: ", metrics[metrics[,1]==x[1], 2], sep=" ")
  }
  desc <- paste("Description: ", x[3], sep=" ")
  paste(name, id, value, desc, sep="\n\n") 
}
cat( paste( apply(metrics_ref, 1, f_m), sep="" ) )
```


# Attributes

\begin{centering}

```{r table_attrs, results='asis'}
print( xtable( attributes, 
       align="|c|p{5cm}|p{3cm}|"), comment=FALSE,
       include.rownames=FALSE, include.colnames=TRUE, 
       floating=FALSE, size="\\scriptsize" )
```

\end{centering}

```{r attrs_list, results='asis', echo=FALSE}
f_a <- function(x, output) {
  name <- paste("\n\n## ", attrs_ref[attrs_ref[,1]==x[1], 2], sep=" ")
  id <- paste("ID: ", x[1], sep=" ")
  value <- paste("Value: ", attributes[attributes[,1]==x[1], 2], " / 5 ", sep=" ")
  desc <- paste("Description: ", attrs_ref[attrs_ref[,1]==x[1], 3], sep=" ")
  paste(name, id, value, desc, sep="\n\n") 
}
cat( paste( apply(attributes, 1, f_a), sep="" ) )
```


# Git analysis

```{r git}
file.evol = paste("../../../../projects/", project.id, "/output/",
	  project.id, "_git_commits.csv", sep="")

evol <- read.csv(file=file.evol, header=T)

commits_vol <- sum(evol$commits)
authors_vol <- sum(evol$authors)

evol_xts <- xts(x=evol[,2-3], order.by=as.POSIXct(evol$date))
```

The repository contains a total of ``r commits_vol`` commits made by ``r metrics[metrics[,1]=='SCM_AUTHORS',2]`` authors. The first commit was made on the ``r evol[1,1]`` and the last analysed commits was made on ``r evol[nrow(evol),1]``.

During the last month, there has been ``r metrics[metrics[,1]=='SCM_COMMITS_1M',2]`` commits made by ``r metrics[metrics[,1]=='SCM_AUTHORS_1M',2]`` authors.

## Weekly commits 

```{r git_commits, fig.width=6, fig.height=3}
require(ggthemes)

ep <- endpoints(evol_xts, on = 'weeks')
evol_xts_commits <- period.apply(x=evol_xts[,1], INDEX=ep, FUN=sum)
ggplot(evol_xts_commits, aes(x=index(evol_xts_commits), y=commits)) +
			 geom_line() +
			 theme_tufte() +
			 labs(x="Date", y="Weekly commits",
			      title="Weekly commits for project",
			      caption="Based on data from Alambic")

```

## Weekly authors 

```{r git_authors, fig.width=6, fig.height=3}
evol_xts_authors <- period.apply(x=evol_xts[,2], INDEX=ep, FUN=sum)
ggplot(evol_xts_authors, aes(x=index(evol_xts_authors), y=authors)) +
			 geom_line() +
			 theme_tufte() +
			 labs(x="Date", y="Weekly authors",
			      title="Weekly authors for project",
			      caption="Based on data from Alambic")
```

